focals

### 2023-03-20 scripts/0_whole_game.qmd
first revisions to ncc 2023-03-17

```{r setup}
library(tidyverse)
library(terra)
library(sf)
library(bcmaps)
library(sgsR)
library(exactextractr)

@@

```{r loads}
vlce <- rast("G:/mosaiced/VLCE2.0/LC_Class_HMM_2015_v20_v20.dat")
bcb <- bcmaps::bc_bound() %>%
  vect()

@@

```{r run-focal}
focal_loc <- "G:/mosaiced/focal"

>>>>

```{r setup}
library(tidyverse)
library(terra)
library(sf)
library(bcmaps)
library(sgsR)
library(cols4all)
# library(exactextractr)

@@

```{r loads}
vlce <- rast("F:/mosaiced/VLCE2.0/LC_Class_HMM_2015_v20_v20.dat")
bcb <- bcmaps::bc_bound() %>%
  vect()

@@

```{r run-focal}
focal_loc <- "F:/mosaiced/focal"

### 2023-03-20 scripts/1_bc_focal_processing.qmd
first revisions to ncc 2023-03-17

struct_loc <- here::here("G://", "mosaiced", "structure")

@@

```{r reticulate}
# this does the focal cell processing for all of BC based on the tiles 
# created earlier in this script
library(reticulate)
use_python("C:/Users/evanmuis/Miniconda3/envs/geospatial/python.exe")

@@

focal_save <- here::here("G:/", "mosaiced", "focal")

>>>>

struct_loc <- here::here("F://", "mosaiced", "structure")

@@

```{r reticulate}
# this does the focal cell processing for all of BC based on the tiles 
# created earlier in this script
library(reticulate)
use_python("C:/Users/evanmuis/AppData/Local/miniconda3/envs/geospatial/python.exe")

@@

focal_save <- here::here("F:/", "mosaiced", "focal")
